Determining what makes some TADs unpredictable

### 2019-06-10 Scripts/investigating_misclassified_TADs.Rmd
script for predicting finer bins

### GM12878

####10kb

>>>>

```{r}
misclassified_func <- function(CL, resolution, sampling="smote", predictor="distance", chromosome){
  #reading in whole genome data
	##setting directory specific to cell line and resolution 
	if(CL=="GM12878"){dataset = "gm12878"}else{dataset = "K562"}
	wgd_directory <- paste0("Z:/TAD_data_analysis/",
	                        CL,
							"/",
							resolution,
							"/training_testing/",
							dataset,
							"_",
							resolution,
							".rds")
	whole_genome_dat <- readRDS(wgd_directory)

	#reading in bin data on the whole genome that contains chromosome information
	##setting directory specific to cell line and resolution 
	bd_directory <- paste0("Z:/TAD_data_analysis/",
	                        CL,
							"/",
							resolution,
							"/training_testing/binslist",
							gsub("kb","",resolution),
							"_center.rds")
	binslist_dat <- readRDS(bd_directory)

	#removing duplicate annotations
	if(CL=="GM12878"){
		varstorm = c(names(whole_genome_dat)[grep("Ctcf-", names(whole_genome_dat))][-c(1:4)],
					 names(whole_genome_dat)[grep("Ebf1sc137065-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("P300-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("Pol2-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("Rad21-", names(whole_genome_dat))][-c(1:4)])} else {
		varstorm = c(names(whole_genome_dat)[grep("Atf3-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("Cmyc-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("Ctcf-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("E2f6-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("Max-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("P300-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("Pol2-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("Rad21-", names(whole_genome_dat))][-c(1:4)],
                     names(whole_genome_dat)[grep("Yy1-", names(whole_genome_dat))][-c(1:4)])
					 }

	whole_genome_dat <- whole_genome_dat[,-which(names(whole_genome_dat) %in% varstorm)]

	#reducing the whole genome data to only specific chromosome
	reduce_chr <- tolower(chromosome)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

	#splitting into training and testing
	set.seed(123)
    inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
    train <- chr_specific_dat[inTrainingSet,]
    test <- chr_specific_dat[-inTrainingSet,]

	#reduce predictor space
	if(predictor=="distance"){reduce_predictor = "_dist"}else if(predictor=="oc"){reduce_predictor = "_count"}else{reduce_predictor = "_perc"}

	train <- train[,c(1,grep(reduce_predictor, names(train)))]
	test <- test[,c(1,grep(reduce_predictor, names(test)))]

	#reading in model and making predictions
	model_directory <- paste0("Z:/TAD_data_analysis/",
	                        CL,
							"/",
							resolution,
							"/results_by_chr/",
							chromosome,
							"/",
							"smote/distance/enet/rfModel_noenet.rds")
  rfModel <- readRDS(model_directory)

  predictions <- predict(rfModel, newdata=test)
  preddata <- cbind.data.frame(Prediction = predictions, True=test$y)

  prediction_data <- list(FNdatamelt,TPdatamelt)
  return(prediction_data)
}
```

## Plots

```{r}
allpredictiondata <- rbind.data.frame(prediction_data[[1]],prediction_data[[2]])
allpredictiondata$Prediction <- factor(allpredictiondata$Prediction, levels=c("False Negatives","True Positives"))

#looking at specific annotations
##Ctcf
ggplot(allpredictiondata[grep("Ctcf-",allpredictiondata$variable),], aes(x=value, color=Prediction)) +
  geom_density() +
  scale_color_discrete(name="Prediction Class") +
  ylab("Density") +
  xlab("Log2 Distance") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

##Rad21
ggplot(allpredictiondata[grep("Rad21-",allpredictiondata$variable),], aes(x=value, color=Prediction)) +
  geom_density() +
  scale_color_discrete(name="Prediction Class") +
  ylab("Density") +
  xlab("Log2 Distance") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
